Temporal Semantics to Go: A Complete Run of the FraCaS Test Suite

### 2021-02-07 paper2020/paper_2021.tex
minor typos!

\paragraph{Inference using Coq}
Logical forms are then fed to the Coq
Coq interactive theorem prover (proof assistant). Coq is based on
the calculus of co-inductive constructions~\citep{werner_une_1994} We
do not use any co-induction (or even induction) in this paper, relying
on the pure lambda-calculus inner core of Coq.  Coq is a very powerful
reasoning engine that makes it fit for implementing natural language
semantics.  Coq also supports  dependent typing and 
 subtyping. Both concepts are instrumental in expressing NL
semantics~\citep{chatzikyriakidis_natural_2014}.  Besides, on a more
practical side, it works well for the the task of NLI, when the latter
is formalised as a theorem proving task: its many tactics mean that
many tasks in theorem proving are trivialised. In particular, all
problems of time-intervals inclusion, which occur in every temporal
problems, are solved with Coq's linear arithmetic tactic.

@@

Unicity of action holds only if the aspectual class of the proposition
$P$ is \emph{activity}~\citep{steedman_productions_2000} (which, for our
purposes, includes \emph{achievements} and \emph{accomplishments}).

>>>>

\paragraph{Inference using Coq}
Logical forms are then fed to the 
Coq interactive theorem prover (proof assistant). Coq is based on
the calculus of co-inductive constructions~\citep{werner_une_1994} We
do not use any co-induction (or even induction) in this paper, relying
on the pure lambda-calculus inner core of Coq.  Coq is a very powerful
reasoning engine that makes it fit for implementing natural language
semantics.  Coq also supports  dependent typing and 
 subtyping. Both concepts are instrumental in expressing NL
semantics~\citep{chatzikyriakidis_natural_2014}.  Besides, on a more
practical side, it works well for the the task of NLI, when the latter
is formalised as a theorem proving task: its many tactics mean that
many tasks in theorem proving are trivialised. In particular, all
problems of time-intervals inclusion, which occur in every temporal
problems, are solved with Coq's linear arithmetic tactic.

@@

Unicity of action holds only if the aspectual class of the proposition
$P$ is \emph{activity}~\citep{steedman_productions_2000} (which, for our
purposes, includes \emph{achievements} and \emph{accomplishments as well}).
